### 2020-03-19 paper.tex
Initial Commit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{Assets/fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE templates contain guidance text for composing and formatting papers. Please ensure that all template text is removed from your paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2020-03-19 paper.tex
Add Authors Info

@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-}
+\author{\IEEEauthorblockN{Khaled Amgad\IEEEauthorrefmark{1},
+Mahmoud Mohamad\IEEEauthorrefmark{2}, Muhanad Atef\IEEEauthorrefmark{3} and
+Nader AbdAlGhani\IEEEauthorrefmark{4}}
+\IEEEauthorblockA{Computer Engineering Dept.,
+Faculty of Engineering, Cairo University\\
+Cairo, Egypt\\
+\IEEEauthorrefmark{1}khaled.mohamed98@eng-st.cu.edu.eg,
+\IEEEauthorrefmark{2}mmmacmp@gmail.com,
+\IEEEauthorrefmark{3}muhanad.atef23@gmail.com,
+\IEEEauthorrefmark{4}nader\_abdelghani@hotmail.com}}
 

### 2020-03-19 paper.tex
Make Introduction Section

@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the page limits.
+
+Scheduling is a crucial part in many real-time applications such as scheduling airlines and railways communications, products manufacturing processes, data packets routing in computer networks and pipe networks.
+Operating systems multiprocessing environments are no different than those mediums mentioned, where processes compete over CPU utilization.
+This brought to existence the need for scheduling algorithms to justly assign processes to available CPUs in favour of optimising performance measures, in particular, to maximize overall CPU utilization and throughput, and to minimize response time, waiting time and turnaround time.
+A schedular could be preemptive where it can temporarily interrupt a process without its cooperation and assign the CPU resources to a different process with the intention to assign them back to the former process, such operation is called context switching, or it could be non-preemptive (cooperative) by not being able to context switch between processes.
+Various preemptive and non-preemptive scheduling disciplines exist such as, first come, first serve (FCFS), shortest job first (SJF), shortest remaining time first (SRTF), round-robin (RR), multilevel queue and multilevel feedback queue.
+In FCFS, processes are non-preemptively executed according to their arrival time.
+In SJF, the CPU is assigned to the process with the smallest burst time.
+SRTF is a preemptive version of SJF where at each iteration, the process with the least remaining burst time takes control of the CPU.
+Round-robin preemptively assigns the CPU to each process in the ready queue for a static amount of time called quantum and executes them in an FCFS fashion.
+Multilevel queue algorithm partitions the ready queue into several queues to which processes are perpetually assigned and are executed according to another scheduling algorithm (e.g.
+RR).
+Processes cannot move from one queue to another.
+However, in multilevel feedback queue algorithm, processes that don't terminate in one queue, due to having CPU burst time more than the time quantum assigned to their particular queue, are shifted to a lower priority queue.
+Due to the fact that long processes eventually sink to the lowest priority queue, they are carried out using FCFS to prevent starvation.
+Several papers discuss different methods to optimize the algorithms mentioned, each come with their set of advantages and drawbacks.
+One of many is Paper [], whose approach achieves better average response time but at the cost of hindering the scheduling process due to recalculating time quantum for each queue using a recurrent neural network.
+Our proposed approach implements the best of all worlds regarding paper [] and [] by avoiding each drawback and optimising their advantages.
 

### 2020-03-19 paper.tex
Add Related Work Section

@@
 should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+% \thanks{Identify applicable funding agency here. If none, delete this.}
 }
@@
 
-\section{Ease of Use}
+\section{Related Work}
 
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+Several papers proposed various types of approaches to improve the overall efficiency of the multilevel feedback queue scheduling algorithm.
+The chosen quantum time for each queue plays a major role.
+For instance, in paper [] The highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant which greatly prevents starvation for lower priority processes.
+Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance.
+In paper [6], a new algorithm is presented for solving these drawbacks and minimizing the response time.
+In this algorithm, a Recurrent Neural Network was used to determine both the number of queues and the optimized time quantum value for each queue.
+The RNN generates the most effective model to compute the time quantum value.
+Their proposed intelligent version of the MLFQ promises good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm.
+Our approach uses an optimized version of RR named shortest remaining burst round-robin (SRBRR) as in paper [4] avoids the learning time in paper [6].
+Regarding MLFQ, various approaches have been made and researches have been carried to improve its efficiency.
+Those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority.
+However, our approach deals with starvation not by only having dynamic quantum value but by boosting processes from lower priority queues to higher ones according to a specific policy.
 

### 2020-03-19 paper.tex
Add References and Citations

@@
 Several papers discuss different methods to optimize the algorithms mentioned, each come with their set of advantages and drawbacks.
-One of many is Paper [], whose approach achieves better average response time but at the cost of hindering the scheduling process due to recalculating time quantum for each queue using a recurrent neural network.
-Our proposed approach implements the best of all worlds regarding paper [] and [] by avoiding each drawback and optimising their advantages.
+One of many is \cite{b2}, whose approach achieves better average response time but at the cost of hindering the scheduling process due to recalculating time quantum for each queue using a recurrent neural network.
+Our proposed approach implements the best of all worlds regarding \cite{b1} and \cite{b3} by avoiding each drawback and optimising their advantages.
 
@@
 The chosen quantum time for each queue plays a major role.
-For instance, in paper [] The highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant which greatly prevents starvation for lower priority processes.
+For instance, in \cite{b1} The highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant which greatly prevents starvation for lower priority processes.
 Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance.
-In paper [6], a new algorithm is presented for solving these drawbacks and minimizing the response time.
+In \cite{b2}, an algorithm is presented for solving these drawbacks and minimizing the response time.
 In this algorithm, a Recurrent Neural Network was used to determine both the number of queues and the optimized time quantum value for each queue.
@@
 Their proposed intelligent version of the MLFQ promises good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm.
-Our approach uses an optimized version of RR named shortest remaining burst round-robin (SRBRR) as in paper [4] avoids the learning time in paper [6].
+Our approach uses an optimized version of RR named shortest remaining burst round-robin (SRBRR) as in \cite{b3} avoids the learning time in \cite{b2}.
 Regarding MLFQ, various approaches have been made and researches have been carried to improve its efficiency.
@@
 \begin{thebibliography}{00}
-\bibitem{b1} G.
+\bibitem{b1} H.S.
+Behera, Reena Kumari Naik, Suchilagna Parida, ``Improved multilevel feedback queue scheduling using dynamic time quantum and its performance analysis'', \textit{International Journal of Computer Science and Information Technologies}, vol.
+3, no.
+2, 2012, pp.
+3801-3807.
+\bibitem{b2} MohammadReza EffatParvar, Karim Faez, Mehdi EffatParvar, Mehdi Zarei, Saeed Safari, ``An intelligent MLFQ scheduling algorithm (IMLFQ) with fault tolerant mechanism'', \textit{Sixth International Conference on Intelligent Systems Design and Applications}, vol.
+3, 2006, pp.
+80–85.
+\bibitem{b3} Rakesh Mohanty, H.
+S.
+Behera, Khusbu Patwari, Monisha Dash, ``Design and performance evaluation of a new proposed shortest remaining burst round robin (SRBRR) scheduling algorithm'', \textit{International Symposium on Computer Engineering \& Technology}, vol.
+17, 2010.
+%\bibitem{b1} G.
 Eason, B.
@@
 529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
+% \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+% \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+% \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+% \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+% \bibitem{b6} Y.
 Yorozu, M.
@@
 301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+% \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
 \end{thebibliography}

### 2020-03-19 paper.tex
'Related Work' Minor Modifications

@@
 The chosen quantum time for each queue plays a major role.
-For instance, in \cite{b1} The highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant which greatly prevents starvation for lower priority processes.
+For instance, in \cite{b1}, the highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant which prevents starvation for lower priority processes.
 Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance.
 In \cite{b2}, an algorithm is presented for solving these drawbacks and minimizing the response time.
-In this algorithm, a Recurrent Neural Network was used to determine both the number of queues and the optimized time quantum value for each queue.
-The RNN generates the most effective model to compute the time quantum value.
-Their proposed intelligent version of the MLFQ promises good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm.
-Our approach uses an optimized version of RR named shortest remaining burst round-robin (SRBRR) as in \cite{b3} avoids the learning time in \cite{b2}.
-Regarding MLFQ, various approaches have been made and researches have been carried to improve its efficiency.
-Those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority.
-However, our approach deals with starvation not by only having dynamic quantum value but by boosting processes from lower priority queues to higher ones according to a specific policy.
+In this algorithm, a Recurrent Neural Network (RNN) was used to determine both the number of queues and the optimized time quantum value for each queue.
+The RNN generates an effective model to compute the time quantum value.
+Their proposed intelligent version of the MLFQ offers good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm.
+Our approach proposes an enhanced version of MLFQ using an optimized version of RR named shortest remaining burst round-robin (SRBRR) as in \cite{b3} which avoids the learning and overhead time in \cite{b2}.
+Regarding the various approaches to improve the MLFQ algorithm, those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority.
+Our approach deals with starvation by boosting processes from lower priority queues to higher ones according to a specific policy.
 

### 2020-03-19 paper.tex
Minor Changes

@@
 The chosen quantum time for each queue plays a major role.
-For instance, in \cite{b1}, the highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant which prevents starvation for lower priority processes.
+For instance, in \cite{b1}, the highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant.
 Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance.

### 2020-03-27 paper.tex
"Introduction" Section Fixes

@@
 
-Scheduling is a crucial part in many real-time applications such as scheduling airlines and railways communications, products manufacturing processes, data packets routing in computer networks and pipe networks.
+Scheduling is a crucial part of many real-time applications such as scheduling airlines and railways communications, product manufacturing processes, data packets routing in computer networks and pipe networks.
 Operating systems multiprocessing environments are no different than those mediums mentioned, where processes compete over CPU utilization.
-This brought to existence the need for scheduling algorithms to justly assign processes to available CPUs in favour of optimising performance measures, in particular, to maximize overall CPU utilization and throughput, and to minimize response time, waiting time and turnaround time.
+This brought to existence the need for scheduling algorithms to justly assign processes to available CPUs in favour of optimizing performance measures, in particular, to maximize overall CPU utilization and throughput, and to minimize response time, waiting time and turnaround time.
 A schedular could be preemptive where it can temporarily interrupt a process without its cooperation and assign the CPU resources to a different process with the intention to assign them back to the former process, such operation is called context switching, or it could be non-preemptive (cooperative) by not being able to context switch between processes.
@@
 Processes cannot move from one queue to another.
-However, in multilevel feedback queue algorithm, processes that don't terminate in one queue, due to having CPU burst time more than the time quantum assigned to their particular queue, are shifted to a lower priority queue.
+However, in a multilevel feedback queue algorithm, processes that don't terminate in one queue, due to having CPU burst time more than the time quantum assigned to their particular queue, are shifted to a lower priority queue.
 Due to the fact that long processes eventually sink to the lowest priority queue, they are carried out using FCFS to prevent starvation.
@@
 One of many is \cite{b2}, whose approach achieves better average response time but at the cost of hindering the scheduling process due to recalculating time quantum for each queue using a recurrent neural network.
-Our proposed approach implements the best of all worlds regarding \cite{b1} and \cite{b3} by avoiding each drawback and optimising their advantages.
+Our proposed approach implements the best of all worlds regarding \cite{b1} and \cite{b3} by avoiding each drawback and optimizing their advantages.
 

### 2020-03-27 paper.tex
Add "Proposed Approach" Section

@@
 Our approach deals with starvation by boosting processes from lower priority queues to higher ones according to a specific policy.
+
+\section{Proposed Approach}
+
+For a multilevel feedback queue scheduling algorithm, three parameters should be considered.
+The first being the chosen scheduling algorithm for each queue, especially the last queue as its scheduling algorithm must help treat starvation.
+The second is the criteria according to which a process priority should be increased based on its waiting time in its particular ready-queue, this technique is also known as Aging.
+The third is the criteria according to which a process priority should be decreased.
+In our proposed algorithm, there are 5 queues sorted in ascending order in line with their priority number, 0 being the highest priority and 4 being the lowest.
+Each queue uses a modified version of the round-robin scheduling algorithm stated in \cite{b3}.
+In \cite{b3}, processes are sorted in ascending order according to their burst time and are assigned a time quantum that equals the median burst time of those processes.
+This dynamic quantum time RR algorithm provides better turnaround time and waiting time than the standard static quantum time RR algorithm whose quantum if set too short, leads to many context switches and if set too long, morphs the algorithm into an FCFS algorithm.
+The proposed alteration on the stated algorithm in \cite{b3} is that each queue quantum time isn't exactly the median burst time, but the burst time whose index is shifted from the median value towards the higher burst time values with a step count equal to its queue number, hence, the gradual increase of quantum time as priority decreases.
+For clarification, a queue with priority equal 2 has the following processes denoted by their burst time: 100, 300, 550, 600, 620, 700, 720, 900, 1200, the median value is 620, assuming we are using zero-based numbering, its index equals 4, and since we are in a queue whose priority equals 2, therefore the quantum slice value according to the proposed approach equals the burst value at index 6 (as in 4 + 2) which is 720.
+If the processes of a certain queue didn't terminate after assigning its queue quantum time, they are shifted downwards to the next lower priority queue.
+After introducing new processes into a queue, the quantum time slice is recalculated.
+Processes age whenever they are in a queue whose priority is one less than that currently getting scheduled and satisfies the following inequality:
+\begin{equation}
+1 - \frac{waiting \; time \; of \; P}{burst \; time \; of \; P} < 0.95\label{eq}
+\end{equation}
+
+Those procedures are repeated for all the generated queues until all processes reach the lowest priority queue where they are rescheduled until their completion.
+
+\subsection{Pseudo Code of the Proposed Algorithm}
+
+\subsection{Flow Chart of the Proposed Algorithm}
 

### 2020-03-27 paper.tex
Add "Algorithm" Subsection

@@
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{graphicx}
@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+% \makeatletter
+% % \newcommand\fs@norules{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
+% %     \def\@fs@pre{}%
+% %     \def\@fs@post{}%
+% %     \def\@fs@mid{\kern3pt}%
+% %     \let\@fs@iftopcapt\iftrue}
+% \makeatother
+% \floatstyle{norules}
+% \restylefloat{algorithm}
+
 \begin{document}
@@
 
-\subsection{Pseudo Code of the Proposed Algorithm}
+\subsection{Proposed Algorithm}
 
-\subsection{Flow Chart of the Proposed Algorithm}
+\begin{algorithm}[H]
+    \caption{Enhanced Multilevel FeedBack Queue Scheduling Algorithm}
+    \begin{algorithmic}[1]
+    \Procedure {EMLFQ}{Number of processes $n$, priority of each process $\alpha_{i}$, burst time of each process $\beta_{i}$}
+    % Return  Average waiting time, throughput
+    \Statex Declaration and Initialisation:
+    \State Queue $Q_{i}$ where $i \in \{0, 1, 2, 3, 4\}$, waiting time $\omega_{i} = 0$ of $P_{i}$, quantum time $\Gamma$, quantum time index $\gamma$
+        \For {$i = 0$ to $n$}
+            \State \textbf{Assign} $P_{i}$ to $Q_{\alpha_{i}}$
+        \EndFor
+    \Statex Loop Process:
+        \State $i = 0$
+        \While {$Q_{i}$ is NOT empty}
+            % Aging Processes
+            \For{$j = i + 1$ to $5$}
+                \If{$1-\omega_{\theta}/\beta_{\theta} < 0.95$ for $\theta \in Q_{j}$}
+                    \State \textbf{Promote} $P_{\theta}$ to the current queue $Q_{i}$
+                \EndIf
+            \EndFor
+
+            % Calculating the quantum time value
+            \Statex Calculating the quantum time value:
+            \State $ascending\_sort(\beta_{Q_{i}})$
+            \State $\gamma = Q_{i}.size()/2 + i$
+            \State $\Gamma = \beta_{\gamma}$ where $\beta_{\gamma} \in Q_{i}$
+            % Assigning the quantum value to each process in the queue
+            \Statex Assigning the Quantum Value to each Process:
+            \For{$P_{j}$ in $Q_{i}$}
+                \State $\beta_{j} = \beta_{j} - \Gamma$
+                \If{$\beta_{j} <= 0$}
+                    \State \textbf{Remove} $P_{j}$ from $Q_{i}$
+                \ElsIf {$i < 4$}
+                    \State \textbf{Downgrade} $P_{j}$ to $Q_{i+1}$
+                \EndIf
+            \EndFor
+            % Increment waiting time
+            \Statex Increment Waiting Time:
+            \For{$j = 0$ to $n$}
+                \State $\omega_{j} = \omega_{j} + 1$
+            \EndFor
+            \Statex Increment Queue Index
+            \If{$i < 4$}
+                \State $i = i + 1$
+            \EndIf
+        \EndWhile
+     \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+
+\subsection{Flowchart of the Proposed Algorithm}
 

### 2020-03-28 paper.tex
Modify "Algorithm" Section
Add "Flowchart" Subsection

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
 \usepackage{cite}
@@
 
-% \makeatletter
-% % \newcommand\fs@norules{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
-% %     \def\@fs@pre{}%
-% %     \def\@fs@post{}%
-% %     \def\@fs@mid{\kern3pt}%
-% %     \let\@fs@iftopcapt\iftrue}
-% \makeatother
-% \floatstyle{norules}
-% \restylefloat{algorithm}
+\makeatletter
+\newcommand\fs@norules{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
+    \def\@fs@pre{}%
+    \def\@fs@post{}%
+    \def\@fs@mid{\kern3pt}%
+    \let\@fs@iftopcapt\iftrue}
+\makeatother
+
+\tikzstyle{startstop} = [ellipse,minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
+\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
+\tikzstyle{process} = [rectangle, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=white]
+\tikzstyle{decision} = [diamond, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
 
+\subsection{Pseudocode Flowchart of the Proposed Approach}
+\vspace{5mm}
+\begin{tikzpicture}[node distance=2cm]
+
+    \node (start) [startstop] {Start};
+    \node (in1) [io, below of=start, text width = 2cm] {Read Processes Data};
+    \node (pro1) [process, below of=in1, text width = 3cm] {Assign processes to their respective queue};
+    \node (dec1) [decision, below of=pro1, text width = 2cm, yshift=-1cm] {All queues are empty};
+    \node (end) [startstop, left of=dec1, xshift=-2cm] {End};
+    \node (pro2) [process, below of=dec1, text width= 3cm, yshift = -1cm] {Iterate on non-empty queues $Q$};
+    \node (dec2) [decision, below of=pro2, text width = 2cm, yshift=-1cm] {A process $P_{j}$ in $Q_{i+1}$ is boostable};
+    \node (pro3) [process, left of=dec2, text width= 3cm, xshift= -2.2cm] {Promote $P_{j}$ to $Q_{i}$};
+    \node (pro4) [process, below of=dec2, text width= 3cm, yshift=-1.2cm] {Calculate the quantum time value $\Gamma$ of $Q_{i}$};
+    \node (pro5) [process, below of=pro4, text width= 3cm] {Assign $\Gamma$ to $Q_{i}$ processes};
+    \node (pro6) [process, below of=pro5, text width= 3cm] {Downgrade incomplete processes to $Q_{i+1}\,:\,i+1 < 5$};
+    \node (pro7) [process, below of=pro6, text width= 3cm] {Increment waiting time of $P_{j} \notin Q_{i}$};
+
+    \draw [arrow] (start) -- (in1);
+    \draw [arrow] (in1) -- (pro1);
+    \draw [arrow] (pro1) -- (dec1);
+    \draw [arrow] (dec1) -- node[anchor=west, above] {Yes} (end);
+    \draw [arrow] (dec1) -- node[anchor=south, left] {No} (pro2);
+    \draw [arrow] (pro2) -- (dec2);
+    \draw [arrow] (dec2) -- node[anchor=west,above] {Yes} (pro3);
+    \draw [arrow] (pro3.north) -- ++ (0,1.3) -- ++ (4.2,0);
+    \draw [arrow] (dec2) -- node[anchor=south, left] {No} (pro4);
+    \draw [arrow] (pro4) -- (pro5);
+    \draw [arrow] (pro5) -- (pro6);
+    \draw [arrow] (pro6) -- (pro7);
+    \draw [arrow] (pro7.west) -- ++ (-4.5,0) -- ++(0,16.8) -- ++(6.1,0);
+
+    \end{tikzpicture}
+
 \subsection{Proposed Algorithm}
-
+\floatstyle{norules}
+\restylefloat{algorithm}
 \begin{algorithm}[H]
@@
             \Statex Increment Waiting Time:
-            \For{$j = 0$ to $n$}
+            \For{$j = 0$ to $n$ \textbf{and} $P_{j} \notin Q_{i}$}
                 \State $\omega_{j} = \omega_{j} + 1$
@@
 \end{algorithm}
-
-\subsection{Flowchart of the Proposed Algorithm}
 

### 2020-04-18 paper.tex
Add Most of the "Experimental Analysis" Sub Sections

@@
 \tikzstyle{arrow} = [thick,->,>=stealth]
+
+\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
+\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
 
@@
 \begin{equation}
-1 - \frac{waiting \; time \; of \; P}{burst \; time \; of \; P} < 0.95\label{eq}
+1 - \frac{waiting \; time \; of \; P}{burst \; time \; of \; P} < 0.95\label{eq1}
 \end{equation}
@@
 \end{algorithm}
+
+\section{Experimental Analysis}
+
+\subsection{Assumptions}
+
+The proposed scheduling algorithm is software replicated using Python scripts which simulate scheduling independent CPU-bound processes with predetermined burst time, arrival time and the queue to which they belong on a single processor environment which guarantees that no more than a single process uses the CPU at any arbitrary moment.
+
+\subsection{Experimental Scheme}
+
+On one hand, the input arguments to the proposed algorithm implementation are the number of processes to be scheduled, burst time, arrival time and the queue to which they belong to.
+On the other hand, output parameters are the average waiting time, average turnaround time and throughput.
+The following equations are used to calculate the previously mentioned output parameters:
+
+\begin{equation}
+    Average\; Waiting\; Time =  \frac{Total \; Waiting \; Time}{Number \; of \; Processes} \label{eq2}
+\end{equation}
+
+\begin{equation}
+    Average\; Turnaround\; Time =  \frac{Total \; Turnaround \; Time}{Number \; of \; Processes} \label{eq3}
+\end{equation}
+
+\begin{equation}
+    Throughput =  \frac{Number \; of \; Executed \; Processes}{Total \; Execution \; Time} \label{eq4}
+\end{equation}
+
+\vspace{5mm}
+
+\subsection{Performance Metrics}
+
+As a means to have a concrete viable evaluation of either the proposed algorithm or any other scheduling algorithm, the output parameters are taken into consideration for analysis.
+Since the average waiting time indicates the average time that a  process has to starve for, therefore the lower the average waiting time is the better.
+The same principle applies to the average turnaround time and the number of context switches, as the former implies the average time spent by the process since its arrival time to its completion and the latter costs time as the CPU is assigned back and forth between different processes.
+Contrarily to the prior metrics, the larger the throughput is the better as it indicates the number of processes that are completely executed per unit time.
+
+\subsection{Simulation}
+
+For the sake of showcasing the proposed algorithm, a number of processes, their predetermined burst time and arrival time are taken as input to a Python simulation script.
+Suppose that the input to the script is according to the following table:
+
+\begin{table}[H]
+    \caption{}
+    \centering
+     \begin{tabular}{||c c c c||} 
+     \hline
+     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+     \hline
+     \hline
+     1 & 0 & 60 & 1 \T \B \\ 
+     \hline
+     2 & 0 & 50 & 1 \T \B \\
+     \hline
+     3 & 0 & 40 & 2 \T \B \\
+     \hline
+     4 & 0 & 30 & 2 \T \B \\
+     \hline
+     5 & 0 & 10 & 3 \T \B \\ 
+     \hline
+     6 & 0 & 210 & 3 \T \B \\ 
+     \hline
+     7 & 0 & 200 & 3 \T \B \\ 
+     \hline
+     \end{tabular}
+     \label{table1}
+\end{table}
+
+According to the proposed algorithm, the time quanta calculated are as follows:
+
+\begin{table}[H]
+    \caption{}
+    \centering
+     \begin{tabular}{||c c||} 
+     \hline
+     \textit{\textbf{Queue}} & \textit{\textbf{Quantum Value}} \T \B \\ 
+     \hline
+     \hline
+     1 & 55 \T \B \\ 
+     \hline
+     2 & 40 \T \B \\
+     \hline
+     3 & 615 \T \B \\
+     \hline
+     4 & 0 \T \B \\
+     \hline
+     5 & 0 \T \B \\ 
+     \hline
+     \end{tabular}
+\end{table}
+
+All processes are sorted ascendingly according to their remaining time scheduled in their respective queue through assigning the time quantum calculated for each queue.
+The time spent scheduling a particular queue is the waiting time for the subsequent queues.
+
+The scheduling process goes as follows:
+
+\begin{figure}[H]
+        \begin{center}
+        \begin{tabular}{|c|c|}
+         \hline
+            $P_{2}$ & $P_{1}$\T\B\\ 
+         \hline
+        \end{tabular}
+        \end{center}
+        \begin{center}
+            \begin{tabular}{c c c}
+                   0 & 50 & 105\\ 
+            \end{tabular}
+        \end{center}
+    \caption{$Q_{1}$ Gantt Chart}
+\end{figure}
+
+Considering that each process in $Q_{1}$ is assigned a quantum value of $50$, as we reach the last process in $Q_{1}$, the total time consumed equals $105$, which happens to be the time that all the other processes have to wait for in the subsequent queues hence the increase of their waiting time by $105$ units of time.
+
+\begin{figure}[H]
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|}
+     \hline
+        $P_{1}$ & $P_{5}$ & $P_{4}$ & $P_{3}$\T\B\\ 
+     \hline
+    \end{tabular}
+    \end{center}
+    \begin{center}
+        \begin{tabular}{c c c c c}
+               105 & 110 & 120 & 150 & 190\\ 
+        \end{tabular}
+    \end{center}
+\caption{$Q_{2}$ Gantt Chart}
+\end{figure}
+
+Even though $P_{5}$ is assigned to $Q_{3}$ as in Table \ref{table1}, it was promoted to $Q_{2}$ due to satisfying (\ref{eq1}).
+
+\begin{figure}[H]
+    \begin{center}
+    \begin{tabular}{|c|c|}
+     \hline
+        P7 & P6\T\B\\ 
+     \hline
+    \end{tabular}
+    \end{center}
+    \begin{center}
+        \begin{tabular}{c c c}
+               190 & 390 & 600\\ 
+        \end{tabular}
+    \end{center}
+\caption{$Q_{3}$ Gantt Chart}
+\end{figure}
+
+Whenever processes reach the lowest queue precompletion, they are scheduled using the RR scheduling algorithm with a relatively large quantum time value which is in most cases similar to using the FCFS algorithm because, as the time quantum value of the RR algorithm tends to infinity which could practically be a very large number relative to the available processes remaining time, the algorithm tends to morph into the FCFS algorithm.
+This procedure is repeated until all the processes are finished.
+Simulation results are shown in the table below:
+
+\begin{table}[H]
+    \caption{}
+    \centering
+     \begin{tabular}{||c c c||} 
+     \hline
+     \textit{\textbf{Average Turnaround Time}} & \textit{\textbf{Average Waiting Time}} & \textit{\textbf{Throughput}}\T \B \\ 
+     \hline
+     \hline
+     1 & 0 & 60 \T \B \\ 
+     \hline
+     \end{tabular}
+\end{table}
+
+\subsection{Performance Comparisons}
+
+To assess the performance of the proposed algorithm implementation, a varying number of processes is taken in six different experiments as input to the Python simulation script.
+In each experiment, the output of the proposed algorithm implementation is compared to the output of another scheduling algorithm implementation such as standard MLFQ with static quantum RR and other variants of MLFQ and RR addressed in different papers.
+
+\subsubsection{Experiment 1}
+
+In this experiment, the proposed algorithm results are compared against both a static and a dynamic version of the RR algorithm addressed in \cite{b1}.
+
+\begin{table}[H]
+    \caption{Experiment 1 Input}
+    \centering
+     \begin{tabular}{||c c c c||} 
+     \hline
+     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+     \hline
+     \hline
+     1 & 1 & 25 & 1 \T \B \\ 
+     \hline
+     2 & 5 & 70 & 1 \T \B \\
+     \hline
+     3 & 6 & 84 & 1 \T \B \\
+     \hline
+     4 & 7 & 17 & 1 \T \B \\
+     \hline
+     5 & 8 & 35 & 1 \T \B \\ 
+     \hline
+     \end{tabular}
+     \label{table1}
+\end{table}
+
+\begin{table}[H]
+    \caption{Experiment 1 Results}
+    \centering
+    \begin{tabular}{c c c||}
+    \cline{2-3}
+    \cline{2-3}
+    \multicolumn{1}{c||}{} & \textit{\textbf{Average Turnaround Time}} & \textit{\textbf{Average Waiting Time}}\T \B \\
+    \hline
+    \multicolumn{1}{||c}{\textit{\textbf{Proposed Algorithm}}} & 115 & 68.8 \T \B\\ \hline
+    \multicolumn{1}{||c}{\textit{\textbf{Static RR}}} & 161.4 & 116.2 \T \B\\ \hline
+    \multicolumn{1}{||c}{\textit{\textbf{Dynamic RR}}} & 150.8 & 107.6\T \B\\ \hline
+     \end{tabular}
+\end{table}
 

### 2020-04-19 paper.tex
Finish Paper

@@
 \usepackage{xcolor}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.9}
+
+\pgfplotsset{
+    % #1: index in the group(0,1,2,...)
+    % #2: number of plots of that group
+    bar group size/.style 2 args={
+        /pgf/bar shift={%
+                % total width = n*w + (n-1)*skip
+                % -> subtract half for centering
+                -0.5*(#2*\pgfplotbarwidth + (#2-1)*\pgfkeysvalueof{/pgfplots/bar group skip})  + 
+                % the '0.5*w' is for centering
+                (.5+#1)*\pgfplotbarwidth + #1*\pgfkeysvalueof{/pgfplots/bar group skip}},%
+    },
+    bar group skip/.initial=2pt,
+    plot 0/.style={blue,fill=blue!30!white,mark=none},%
+    plot 1/.style={red,fill=red!30!white,mark=none},%
+    plot 2/.style={brown!60!black,fill=brown!30!white,mark=none},%
+    plot 3/.style={brown!60!black,fill=brown!30!white,mark=none},%
+}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{Conference Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-% \thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{Developed Dynamic Multilevel Feedback Scheduling Algorithm with an Aging Criteria for Starvation Mitigation\\}
 
-\author{\IEEEauthorblockN{Khaled Amgad\IEEEauthorrefmark{1},
-Mahmoud Mohamad\IEEEauthorrefmark{2}, Muhanad Atef\IEEEauthorrefmark{3} and
-Nader AbdAlGhani\IEEEauthorrefmark{4}}
+\author{\IEEEauthorblockN{Nader AbdAlGhani\IEEEauthorrefmark{1}
+Mahmoud Mohamad\IEEEauthorrefmark{2}, Muhanad Atef\IEEEauthorrefmark{3} and Khaled Amgad\IEEEauthorrefmark{4}}
 \IEEEauthorblockA{Computer Engineering Dept.,
@@
 Cairo, Egypt\\
-\IEEEauthorrefmark{1}khaled.mohamed98@eng-st.cu.edu.eg,
+\IEEEauthorrefmark{1}nader\_abdelghani@hotmail.com,
 \IEEEauthorrefmark{2}mmmacmp@gmail.com,
 \IEEEauthorrefmark{3}muhanad.atef23@gmail.com,
-\IEEEauthorrefmark{4}nader\_abdelghani@hotmail.com}}
+\IEEEauthorrefmark{4}khaled.mohamed98@eng-st.cu.edu.eg}}
 
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+    Several scheduling algorithms are discussed in this paper with a certain objective in mind, to improve the performance of the Multilevel Feedback Queue (MLFQ) algorithm including the Round Robin (RR) algorithm as the latter is used to schedule the processes present in the queues of the former.
+Just as any scheduling algorithm, the standard MLFQ algorithm comes with its drawbacks which stem from the methodology used to calculate each queue quantum time value and the policies used to decide whether a process should be promoted or have its priority decreased.
+We have introduced an enhanced version of the MLFQ algorithm which computes each queue quantum value by multiplying the median burst time value by a factor of the queue level number, hence the increase of quantum value as priority decreases.
+This proposed approach also guarantees priority boosting whenever a process waiting time exceeds a certain threshold relative to its remaining time.
+Simulation performance analysis shows promising results in terms of decreasing the average turnaround time and the average waiting time.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+Operating systems scheduling, Multilevel feedback queue scheduling, Average turnaround time, Average waiting time, Process Aging, Round-robin scheduling.
 \end{IEEEkeywords}
@@
      \hline
-     \textit{\textbf{Average Turnaround Time}} & \textit{\textbf{Average Waiting Time}} & \textit{\textbf{Throughput}}\T \B \\ 
+     \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}} & \textit{\textbf{Throughput}}\T \B \\ 
      \hline
      \hline
-     1 & 0 & 60 \T \B \\ 
+     230 & 144.3 & 0.011667 \T \B \\ 
      \hline
@@
 
-In this experiment, the proposed algorithm results are compared against both a static and a dynamic version of the RR algorithm addressed in \cite{b1}.
+In this experiment, the proposed algorithm is compared against an MLFQ algorithm stated in \cite{b4} that uses a static version of the RR algorithm for scheduling each queue and another variant that uses a dynamic version of the RR algorithm for doing so.
 
@@
     \centering
-    \begin{tabular}{c c c||}
-    \cline{2-3}
-    \cline{2-3}
-    \multicolumn{1}{c||}{} & \textit{\textbf{Average Turnaround Time}} & \textit{\textbf{Average Waiting Time}}\T \B \\
+    \begin{tabular}{||c c c||}
         \hline
-    \multicolumn{1}{||c}{\textit{\textbf{Proposed Algorithm}}} & 115 & 68.8 \T \B\\ \hline
-    \multicolumn{1}{||c}{\textit{\textbf{Static RR}}} & 161.4 & 116.2 \T \B\\ \hline
-    \multicolumn{1}{||c}{\textit{\textbf{Dynamic RR}}} & 150.8 & 107.6\T \B\\ \hline
+        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
+    \hline
+    \hline
+    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
+    \textbf{Dynamic RR MLFQ} & 150.8 & 107.6\T \B\\ \hline
+    \textbf{Static RR MLFQ} & 161.4 & 116.2 \T \B\\ \hline
      \end{tabular}
@@
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\subsubsection{Experiment 2}
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+In this experiment, the proposed algorithm is compared against an MLFQ algorithm stated in \cite{b4} that uses a static version of the SJFRR algorithm for scheduling each queue and another variant that uses a dynamic version of the SJFRR algorithm for doing so.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
+\begin{table}[H]
+    \caption{Experiment 2 Input}
+    \centering
+     \begin{tabular}{||c c c c||} 
      \hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
      \hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
      \hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+     1 & 1 & 25 & 1 \T \B \\ 
+     \hline
+     2 & 5 & 70 & 1 \T \B \\
+     \hline
+     3 & 6 & 84 & 1 \T \B \\
+     \hline
+     4 & 7 & 17 & 1 \T \B \\
+     \hline
+     5 & 8 & 35 & 1 \T \B \\ 
+     \hline
      \end{tabular}
-\label{tab1}
-\end{center}
+     \label{table1}
 \end{table}
 
-\begin{figure}[htbp]
-\centerline{\includegraphics{Assets/fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
+\begin{table}[H]
+    \caption{Experiment 2 Results}
+    \centering
+    \begin{tabular}{||c c c||}
+        \hline
+        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
+    \hline
+    \hline
+    \textbf{Proposed Algorithm} & 115 & 68.8 \T \B\\ \hline
+    \textbf{Dyn. SJFRR MLFQ} & 134 & 91.8\T \B\\ \hline
+    \textbf{Stat. SJFRRMLFQ} & 143.4 & 98.2 \T \B\\ \hline
+     \end{tabular}
+\end{table}
+
+\subsubsection{Experiment 3}
+
+In this experiment, the proposed algorithm is compared against an MLFQ algorithm stated in \cite{b5} that uses a static version of the SJFRR algorithm for scheduling each queue and another variant that uses a dynamic version of the SJFRR algorithm for doing so.
+
+\begin{table}[H]
+    \caption{Experiment 3 Input}
+    \centering
+     \begin{tabular}{||c c c c||} 
+     \hline
+     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+     \hline
+     \hline
+     1 & 0 & 8 & 1 \T \B \\ 
+     \hline
+     2 & 3 & 133 & 3 \T \B \\
+     \hline
+     3 & 2 & 21 & 2 \T \B \\
+     \hline
+     4 & 8 & 39 & 2 \T \B \\
+     \hline
+     5 & 19 & 67 & 2 \T \B \\ 
+     \hline
+     6 & 33 & 114 & 3 \T \B \\ 
+     \hline
+     7 & 33 & 54 & 2 \T \B \\ 
+     \hline
+     \end{tabular}
+     \label{table1}
+\end{table}
+
+\begin{table}[H]
+    \caption{Experiment 3 Results}
+    \centering
+    \begin{tabular}{||c c c||}
+        \hline
+        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
+    \hline
+    \hline
+    \textbf{Proposed Algorithm} & 151 & 88.7 \T \B\\ \hline
+    \textbf{Dyn. SJFRR MLFQ} & 252 & 119 \T \B\\ \hline
+    \textbf{Stat. SJFRR MLFQ} & 351 & 228 \T \B\\ \hline
+     \end{tabular}
+\end{table}
+
+\subsubsection{Experiment 4}
+
+In this experiment, the proposed algorithm is compared against different variants of the MLFQ algorithm that are stated in \cite{b6}: standard MLFQ, a priority-based MLFQ and a vague logic-based MLFQ algorithm.
+
+\begin{table}[H]
+    \caption{Experiment 4 Input}
+    \centering
+     \begin{tabular}{||c c c c||} 
+     \hline
+     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+     \hline
+     \hline
+     1 & 0 & 40 & 1 \T \B \\ 
+     \hline
+     2 & 0 & 30 & 1 \T \B \\
+     \hline
+     3 & 0 & 50 & 1 \T \B \\
+     \hline
+     4 & 2 & 70 & 1 \T \B \\
+     \hline
+     5 & 4 & 25 & 1 \T \B \\ 
+     \hline
+     6 & 6 & 60 & 1 \T \B \\ 
+     \hline
+     7 & 7 & 45 & 1 \T \B \\ 
+     \hline
+     \end{tabular}
+     \label{table1}
+\end{table}
+
+\begin{table}[H]
+    \caption{Experiment 4 Results}
+    \centering
+    \begin{tabular}{||c c c||}
+        \hline
+        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
+    \hline
+    \hline
+    \textbf{Proposed Algorithm} & 185.85 & 140.14 \T \B\\ \hline
+    \textbf{VMLFQ} & 190 & 170 \T \B\\ \hline
+    \textbf{MLFQ} & 232.14 & 175 \T \B\\ \hline
+    \textbf{PMLFQ} & 240 & 180 \T \B\\ \hline
+     \end{tabular}
+\end{table}
+
+\subsubsection{Experiment 5}
+
+This experiment is the same as the previous one but with a different input test case.
+
+\begin{table}[H]
+    \caption{Experiment 5 Input}
+    \centering
+     \begin{tabular}{||c c c c||} 
+     \hline
+     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+     \hline
+     \hline
+     1 & 0 & 90 & 1 \T \B \\ 
+     \hline
+     2 & 0 & 30 & 1 \T \B \\
+     \hline
+     3 & 0 & 28 & 1 \T \B \\
+     \hline
+     4 & 0 & 57 & 1 \T \B \\
+     \hline
+     5 & 0 & 73 & 1 \T \B \\ 
+     \hline
+     6 & 0 & 19 & 1 \T \B \\ 
+     \hline
+     7 & 0 & 42 & 1 \T \B \\ 
+     \hline
+     8 & 0 & 67 & 1 \T \B \\ 
+     \hline
+     \end{tabular}
+     \label{table1}
+\end{table}
+
+\begin{table}[H]
+    \caption{Experiment 5 Results}
+    \centering
+    \begin{tabular}{||c c c||}
+        \hline
+        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
+    \hline
+    \hline
+    \textbf{Proposed Algorithm} & 212.5 & 161.75 \T \B\\ \hline
+    \textbf{VMLFQ} & 260 & 225 \T \B\\ \hline
+    \textbf{MLFQ} & 290 & 240 \T \B\\ \hline
+    \textbf{PMLFQ} & 300 & 245 \T \B\\ \hline
+     \end{tabular}
+\end{table}
+
+\subsubsection{Experiment 6}
+
+In this experiment, the proposed algorithm is compared against two variants of the RR algorithm stated in \cite{b3}.
+The first is a static version of the RR algorithm with a constant quantum value of $25$ for scheduling each queue while the second uses a dynamic version of the RR algorithm called SRBRR for doing so.
+
+\begin{table}[H]
+    \caption{Experiment 6 Input}
+    \centering
+     \begin{tabular}{||c c c c||} 
+     \hline
+     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+     \hline
+     \hline
+     1 & 0 & 13 & 1 \T \B \\ 
+     \hline
+     2 & 0 & 35 & 1 \T \B \\
+     \hline
+     3 & 0 & 46 & 1 \T \B \\
+     \hline
+     4 & 0 & 63 & 1 \T \B \\
+     \hline
+     5 & 0 & 97 & 1 \T \B \\ 
+     \hline
+     \end{tabular}
+     \label{table1}
+\end{table}
+
+\begin{table}[H]
+    \caption{Experiment 6 Results}
+    \centering
+    \begin{tabular}{||c c c||}
+        \hline
+        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
+    \hline
+    \hline
+    \textbf{Proposed Algorithm} & 113.2 & 62.4 \T \B\\ \hline
+    \textbf{Dynamic SRBRR} & 122.4 & 71.6 \T \B\\ \hline
+    \textbf{Static RR} & 148.2 & 97.4 \T \B\\ \hline
+     \end{tabular}
+\end{table}
+
+\subsubsection{Experiment 7}
+
+This experiment is the same as the previous one but with a different input test case.
+Note that for this test case, a process queue number is irrelevant to both RR algorithm and SRBRR algorithm mentioned in \cite{b3}.
+
+\begin{table}[H]
+    \caption{Experiment 7 Input}
+    \centering
+     \begin{tabular}{||c c c c||} 
+     \hline
+     \textit{\textbf{Process}} & \textit{\textbf{Arrival Time}} & \textit{\textbf{Burst Time}} & \textit{\textbf{Queue}} \T \B \\ 
+     \hline
+     \hline
+     1 & 0 & 54 & 1 \T \B \\ 
+     \hline
+     2 & 0 & 99 & 3 \T \B \\
+     \hline
+     3 & 0 & 5 & 2 \T \B \\
+     \hline
+     4 & 0 & 27 & 2 \T \B \\
+     \hline
+     5 & 0 & 32 & 2 \T \B \\ 
+     \hline
+     \end{tabular}
+     \label{table1}
+\end{table}
+
+\begin{table}[H]
+    \caption{Experiment 7 Results}
+    \centering
+    \begin{tabular}{||c c c||}
+        \hline
+        \textit{\textbf{Algorithm}} & \textit{\textbf{Avg. Turnaround Time}} & \textit{\textbf{Avg. Waiting Time}}\T \B \\
+    \hline
+    \hline
+    \textbf{Dynamic SRBRR} & 93.6 & 50.2 \T \B\\ \hline
+    \textbf{Proposed Algorithm} & 106.8 & 63.4 \T \B\\ \hline
+    \textbf{Static RR} & 152.2 & 108.8 \T \B\\ \hline
+     \end{tabular}
+\end{table}
+
+\subsection{Observation}
+From the above simulations of different test cases and multiple performance comparisons that involved as many as 11 different scheduling algorithms not including this paper algorithm, it is clear that the average turnaround time and the average waiting time of the proposed algorithm is less than or – in few occasions  – nearly equal to those of the stated algorithms.
+With that said, the proposed algorithm is arguably advantageous over those algorithms, considering even the case in which it underperformed compared to the SRBRR algorithm, it is still favourable due to the capability to separate processes into categories based on their need for the processor and other advantages of the MLFQ algorithm.The performance of the proposed algorithm compared to other algorithms is further illustrated in the graphs below:
+
+\begin{figure}[H]
+    \begin{center}
+\begin{tikzpicture}
+    \begin{axis}[
+        width=0.475*\textwidth,
+        symbolic x coords={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
+        ylabel=Avg. Turnaround Time,
+        enlargelimits=0.15,
+        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=1},
+        ybar,
+        xtick={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
+        x tick label style={rotate=45,anchor=east},
+        bar width=3pt,
+        cycle list name=color list
+    ]
+
+    \addplot[plot 0,bar group size={0}{3}, red]
+    coordinates {(Exp. 1,115) (Exp. 2,115) (Exp. 3,151) (Exp. 6,113.2) (Exp. 7,106.8)};
+    \addplot[plot 1,bar group size={1}{3}, green]
+    coordinates {(Exp. 1,150.8)};
+    \addplot[plot 2,bar group size={2}{3}, blue]
+    coordinates {(Exp. 1,161.4)};
+
+    \addplot[plot 1,bar group size={1}{3}, black]
+    coordinates {(Exp. 2,134)};
+    \addplot[plot 2,bar group size={2}{3}, brown]
+    coordinates {(Exp. 2,143.4)};
+
+    \addplot[plot 1,bar group size={1}{3}, teal]
+    coordinates {(Exp. 3,252)};
+    \addplot[plot 2,bar group size={2}{3}, violet]
+    coordinates {(Exp. 3,351)};
+
+    \addplot[plot 0,bar group size={0}{4}, red]
+    coordinates {(Exp. 4,185.85) (Exp. 5,212.5)};
+    \addplot[plot 1,bar group size={1}{4}, lime]
+    coordinates {(Exp. 4,190) (Exp. 5,260)};
+    \addplot[plot 2,bar group size={2}{4}, orange]
+    coordinates {(Exp. 4,232.14) (Exp. 5,290)};
+    \addplot[plot 3,bar group size={3}{4}, olive]
+    coordinates {(Exp. 4,240) (Exp. 5,300)};
+
+    \addplot[plot 1,bar group size={1}{3}, cyan]
+    coordinates {(Exp. 6,122.4) (Exp. 7,93.6)};
+    \addplot[plot 2,bar group size={2}{3}, magenta]
+    coordinates {(Exp. 6,148.2) (Exp. 7,152.2)};
+
+    \end{axis}
+\end{tikzpicture}
+\end{center}
+\caption{Comparison graph for average turnaround time}
 \end{figure}
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+\begin{figure}[H]
+    \begin{center}
+\begin{tikzpicture}
+    \begin{axis}[
+        width=0.475*\textwidth,
+        symbolic x coords={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
+        ylabel=Avg. Waiting Time,
+        enlargelimits=0.15,
+        legend style={at={(0.5,-0.25)}, anchor=north,legend columns=1},
+        ybar,
+        xtick={Exp. 1,Exp. 2,Exp. 3,Exp. 4,Exp. 5,Exp. 6,Exp. 7},
+        x tick label style={rotate=45,anchor=east},
+        bar width=3pt,
+        cycle list name=color list
+    ]
 
-\section*{Acknowledgment}
+    \addplot[plot 0,bar group size={0}{3}, red]
+    coordinates {(Exp. 1,68.8) (Exp. 2,68.8) (Exp. 3,88.7) (Exp. 6,62.4) (Exp. 7,63.4)};
+    \addplot[plot 1,bar group size={1}{3}, green]
+    coordinates {(Exp. 1,107.6)};
+    \addplot[plot 2,bar group size={2}{3}, blue]
+    coordinates {(Exp. 1,116.2)};
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+    \addplot[plot 1,bar group size={1}{3}, black]
+    coordinates {(Exp. 2,91.8)};
+    \addplot[plot 2,bar group size={2}{3}, brown]
+    coordinates {(Exp. 2,98.2)};
 
-\section*{References}
+    \addplot[plot 1,bar group size={1}{3}, teal]
+    coordinates {(Exp. 3,119)};
+    \addplot[plot 2,bar group size={2}{3}, violet]
+    coordinates {(Exp. 3,228)};
 
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+    \addplot[plot 0,bar group size={0}{4}, red]
+    coordinates {(Exp. 4,140.14) (Exp. 5,161.75)};
+    \addplot[plot 1,bar group size={1}{4}, lime]
+    coordinates {(Exp. 4,170) (Exp. 5,225)};
+    \addplot[plot 2,bar group size={2}{4}, orange]
+    coordinates {(Exp. 4,175) (Exp. 5,240)};
+    \addplot[plot 3,bar group size={3}{4}, olive]
+    coordinates {(Exp. 4,180) (Exp. 5,245)};
 
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
+    \addplot[plot 1,bar group size={1}{3}, cyan]
+    coordinates {(Exp. 6,71.6) (Exp. 7,50.2)};
+    \addplot[plot 2,bar group size={2}{3}, magenta]
+    coordinates {(Exp. 6,97.2) (Exp. 7,108.8)};
 
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
+    \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn.
+SJFRR MLFQ of \cite{b4},  Stat.
+SJFRR MLFQ of \cite{b4}, Dyn.
+SJFRR MLFQ of \cite{b5}, Stat.
+SJFRR MLFQ of \cite{b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
+    \end{axis}
+\end{tikzpicture}
+\end{center}
+\caption{Comparison graph for average waiting time}
+\end{figure}
 
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+\section{Conclusion and Future Work}
+
+The goal of this paper is to tackle different shortcomings associated with the standard MLFQ scheduling algorithm as well as its variants discussed in several papers.
+To resolve those deficiencies, we introduced different adjustable policies and techniques and it is evidently clear that those methods yield better CPU performance and optimize utilization by reducing the average waiting time as well as the average turnaround time.
+Despite experimenting numerous combinations of the parameters and scheduling policies by which an MLFQ algorithm operates, we can say that there is yet a large room for experiment and improvement through finding better methods and policies to make the algorithm more adaptable to the nature of the submitted processes and overall more enhanced.
 
 \begin{thebibliography}{00}
+
 \bibitem{b1} H.S.
@@
 3801-3807.
+
 \bibitem{b2} MohammadReza EffatParvar, Karim Faez, Mehdi EffatParvar, Mehdi Zarei, Saeed Safari, ``An intelligent MLFQ scheduling algorithm (IMLFQ) with fault tolerant mechanism'', \textit{Sixth International Conference on Intelligent Systems Design and Applications}, vol.
@@
 80–85.
+
 \bibitem{b3} Rakesh Mohanty, H.
@@
 17, 2010.
-%\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-% \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-% \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-% \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-% \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-% \bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-% \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+
+\bibitem{b4} S.
+K.
+Dwivedi and R.
+Gupta, ``A simulator based performance analysis of multilevel feedback queue scheduling'', \textit{2014 International Conference on Computer and Communication Technology (ICCCT)}, Allahabad, 2014, pp.
+341-346.
+
+\bibitem{b5} Malhar Thombare, Rajiv Sukhwani, Priyam Shah, Sheetal Chaudhari, Pooja Raundale, ``Efficient implementation of multilevel feedback queue scheduling'', \textit{2016 International Conference on Wireless Communications, Signal Processing and Networking (WiSPNET)}, Chennai, 2016, pp.
+1950–1954.
+
+\bibitem{b6} S. Raheja, R. Dadhich, and S. Rajpalc, ``Designing of vague logic based multilevel feedback queue scheduler'', \textit{Egyptian Informatics Journal}, vol. 17, 2016, pp. 125-137.
+
+\bibitem{b7} A.
+Alsheikhy, R.
+Ammar and R.
+Elfouly, ``An improved dynamic Round Robin scheduling algorithm based on a variant quantum time'', \textit{2015 11th International Computer Engineering Conference (ICENCO)}, Cairo, 2015, pp.
+98-104.
+
+\bibitem{b8} M.
+K.
+Mishra and F.
+Rashid, ``An improved round robin CPU scheduling algorithm with varying time quantum'', \textit{International Journal of Computer Science, Engineering and Applications  (IJCSEA)}, vol.
+4, 2014.
+
+\bibitem{b9} A.
+Singh, P.
+Goyal and S.
+Batra, ``An optimized round robin scheduling algorithm for CPU scheduling'', \textit{International Journal on Computer Science and Engineering}, 2010, pp.
+2383-2385.
+
+\bibitem{b10} Dipto Biswas, Md.
+Samsuddoha, ``Determining proficient time quantum to  improve the performance  of  round  robin  scheduling  algorithm'', \textit{International  Journal  of  Modern  Education  and  Computer Science(IJMECS)}, vol.
+11, 2019, pp.
+33-40.
+
+\bibitem{b11} K.
+Hoganson and J.
+Brown, ``Real-time scheduling with MLFQ-RT multilevel feedback queue with starvation mitigation'', \textit{2017 International Conference on Engineering, Technology and Innovation (ICE/ITMC)}, Funchal, 2017, pp.
+155-160.
+
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE templates contain guidance text for composing and formatting papers.
-Please ensure that all template text is removed from your paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 

### 2020-04-19 paper.tex
Revision #1

@@
 \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{tikz}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \title{Developed Dynamic Multilevel Feedback Scheduling Algorithm with an Aging Criteria for Starvation Mitigation\\}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AUTHORS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
@@
 Just as any scheduling algorithm, the standard MLFQ algorithm comes with its drawbacks which stem from the methodology used to calculate each queue quantum time value and the policies used to decide whether a process should be promoted or have its priority decreased.
-We have introduced an enhanced version of the MLFQ algorithm which computes each queue quantum value by multiplying the median burst time value by a factor of the queue level number, hence the increase of quantum value as priority decreases.
+To undertake those shortcomings, we have introduced an enhanced version of the MLFQ algorithm which computes each queue quantum value by multiplying the median of the ascendingly ordered burst time values by a factor of the queue level number, hence the increase of quantum value as priority decreases.
 This proposed approach also guarantees priority boosting whenever a process waiting time exceeds a certain threshold relative to its remaining time.
@@
 \end{abstract}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% KEY WORDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
@@
 Scheduling is a crucial part of many real-time applications such as scheduling airlines and railways communications, product manufacturing processes, data packets routing in computer networks and pipe networks.
-Operating systems multiprocessing environments are no different than those mediums mentioned, where processes compete over CPU utilization.
+Operating systems multiprocessing environments are no different from those mediums mentioned, where processes compete over CPU utilization.
 This brought to existence the need for scheduling algorithms to justly assign processes to available CPUs in favour of optimizing performance measures, in particular, to maximize overall CPU utilization and throughput, and to minimize response time, waiting time and turnaround time.
@@
 However, in a multilevel feedback queue algorithm, processes that don't terminate in one queue, due to having CPU burst time more than the time quantum assigned to their particular queue, are shifted to a lower priority queue.
-Due to the fact that long processes eventually sink to the lowest priority queue, they are carried out using FCFS to prevent starvation.
+Due to the fact that long processes eventually sink to the lowest priority queue, they are conventionally carried out using FCFS to prevent starvation.
 Several papers discuss different methods to optimize the algorithms mentioned, each come with their set of advantages and drawbacks.
 One of many is \cite{b2}, whose approach achieves better average response time but at the cost of hindering the scheduling process due to recalculating time quantum for each queue using a recurrent neural network.
-Our proposed approach implements the best of all worlds regarding \cite{b1} and \cite{b3} by avoiding each drawback and optimizing their advantages.
+In this paper, we attempted to implement the best of all worlds.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RELATED WORK %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The chosen quantum time for each queue plays a major role.
-For instance, in \cite{b1}, the highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant.
 Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance.
-In \cite{b2}, an algorithm is presented for solving these drawbacks and minimizing the response time.
-In this algorithm, a Recurrent Neural Network (RNN) was used to determine both the number of queues and the optimized time quantum value for each queue.
+In \cite{b2}, an algorithm is introduced for minimizing the response time.
+In this algorithm, a Recurrent Neural Network (RNN) is used to determine both the number of queues and the optimized time quantum value for each queue.
 The RNN generates an effective model to compute the time quantum value.
 Their proposed intelligent version of the MLFQ offers good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm.
-Our approach proposes an enhanced version of MLFQ using an optimized version of RR named shortest remaining burst round-robin (SRBRR) as in \cite{b3} which avoids the learning and overhead time in \cite{b2}.
+Our approach proposes an improved version of MLFQ that utilizes an altered version of RR named shortest remaining burst round-robin (SRBRR) introduced in \cite{b3} which avoids the cost of learning time and overhead time in \cite{b2}.
 Regarding the various approaches to improve the MLFQ algorithm, those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority.
-Our approach deals with starvation by boosting processes from lower priority queues to higher ones according to a specific policy.
+Our approach also deals with starvation by boosting processes from lower priority queues to higher ones according to certain criteria.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROPOSED APPROACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-For a multilevel feedback queue scheduling algorithm, three parameters should be considered.
-The first being the chosen scheduling algorithm for each queue, especially the last queue as its scheduling algorithm must help treat starvation.
-The second is the criteria according to which a process priority should be increased based on its waiting time in its particular ready-queue, this technique is also known as Aging.
-The third is the criteria according to which a process priority should be decreased.
-In our proposed algorithm, there are 5 queues sorted in ascending order in line with their priority number, 0 being the highest priority and 4 being the lowest.
+For a multilevel feedback queue scheduling algorithm, three parameters are considered.
+The first is the chosen scheduling algorithm for each queue, especially the last queue as its scheduling algorithm is expected to treat starvation.
+The second is the criteria according to which a process is promoted, this technique is also known as Aging.
+The third is the criteria according to which a process is demoted.
+In our proposed algorithm, there are 5 queues sorted in ascending order in line with their priority number, 1 being the highest priority and 5 being the lowest.
 Each queue uses a modified version of the round-robin scheduling algorithm stated in \cite{b3}.
 In \cite{b3}, processes are sorted in ascending order according to their burst time and are assigned a time quantum that equals the median burst time of those processes.
-This dynamic quantum time RR algorithm provides better turnaround time and waiting time than the standard static quantum time RR algorithm whose quantum if set too short, leads to many context switches and if set too long, morphs the algorithm into an FCFS algorithm.
-The proposed alteration on the stated algorithm in \cite{b3} is that each queue quantum time isn't exactly the median burst time, but the burst time whose index is shifted from the median value towards the higher burst time values with a step count equal to its queue number, hence, the gradual increase of quantum time as priority decreases.
-For clarification, a queue with priority equal 2 has the following processes denoted by their burst time: 100, 300, 550, 600, 620, 700, 720, 900, 1200, the median value is 620, assuming we are using zero-based numbering, its index equals 4, and since we are in a queue whose priority equals 2, therefore the quantum slice value according to the proposed approach equals the burst value at index 6 (as in 4 + 2) which is 720.
-If the processes of a certain queue didn't terminate after assigning its queue quantum time, they are shifted downwards to the next lower priority queue.
+This algorithm provides better turnaround time and waiting time than the standard static quantum RR algorithm whose quantum, if set too short, leads to many context switches and, if set too long, morphs the algorithm into an FCFS algorithm.
+The proposed alteration on the stated algorithm in \cite{b3} is that each queue quantum time equals the median burst time multiplied by a factor matching the queue number.
+Hence, the gradual increase of quantum time as priority decreases.
+For clarification, a queue with priority equal $2$ has the following processes denoted by their burst time: $100$, $300$, $550$, $600$, $620$, $700$, $720$, $900$ and $1200$, the median value is $620$, since we are in a queue whose priority equals $2$, therefore the quantum slice value according to the proposed approach equals $1240$ as in $620 * 2$.
+If processes of a certain queue didn't terminate after assigning the quantum time value, they are shifted to the next lower priority queue.
 After introducing new processes into a queue, the quantum time slice is recalculated.
@@
 \begin{equation}
-1 - \frac{waiting \; time \; of \; P}{burst \; time \; of \; P} < 0.95\label{eq1}
+\frac{waiting \; time \; of \; P}{burst \; time \; of \; P} >= 1\label{eq1}
 \end{equation}
@@
 Those procedures are repeated for all the generated queues until all processes reach the lowest priority queue where they are rescheduled until their completion.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FLOWCHART %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     \end{tikzpicture}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALGORITHM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTAL ANALYSIS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Experimental Analysis}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ASSUMPTIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The proposed scheduling algorithm is software replicated using Python scripts which simulate scheduling independent CPU-bound processes with predetermined burst time, arrival time and the queue to which they belong on a single processor environment which guarantees that no more than a single process uses the CPU at any arbitrary moment.
+The proposed scheduling algorithm is software simulated using a Python script which simulates scheduling independent CPU-bound processes on a single processor environment which guarantees that no more than a single process is getting scheduled at any arbitrary moment.
+Each process is assumed to have its own predetermined burst time, arrival time and the queue to which each one belongs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% I/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-On one hand, the input arguments to the proposed algorithm implementation are the number of processes to be scheduled, burst time, arrival time and the queue to which they belong to.
+On one hand, the input arguments to the proposed algorithm implementation are the number of processes to be scheduled, their burst time, their arrival time and the queue where each one belongs.
 On the other hand, output parameters are the average waiting time, average turnaround time and throughput.
@@
 
-\vspace{5mm}
+\vspace{4mm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PERFORMANCE METRICS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-As a means to have a concrete viable evaluation of either the proposed algorithm or any other scheduling algorithm, the output parameters are taken into consideration for analysis.
-Since the average waiting time indicates the average time that a  process has to starve for, therefore the lower the average waiting time is the better.
+As a means to have a concrete, viable evaluation of either the proposed algorithm or any other scheduling algorithm, the output parameters are taken into consideration for analysis.
+Since the average waiting time indicates the average time that a  process had to starve for, therefore the lower the average waiting time is the better.
 The same principle applies to the average turnaround time and the number of context switches, as the former implies the average time spent by the process since its arrival time to its completion and the latter costs time as the CPU is assigned back and forth between different processes.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SIMULATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Simulation}
 
-For the sake of showcasing the proposed algorithm, a number of processes, their predetermined burst time and arrival time are taken as input to a Python simulation script.
+For the sake of showcasing the proposed algorithm, a number of processes, their predetermined burst time values and their arrival time values are taken as input to the Python simulation script.
 Suppose that the input to the script is according to the following table:
@@
 
-All processes are sorted ascendingly according to their remaining time scheduled in their respective queue through assigning the time quantum calculated for each queue.
-The time spent scheduling a particular queue is the waiting time for the subsequent queues.
+All processes are sorted in ascending order according to their remaining time and are scheduled by assigning the time quantum calculated for their respective queue.
+The time spent scheduling a particular queue is the waiting time for its subsequent queues.
 
@@
 
-Considering that each process in $Q_{1}$ is assigned a quantum value of $50$, as we reach the last process in $Q_{1}$, the total time consumed equals $105$, which happens to be the time that all the other processes have to wait for in the subsequent queues hence the increase of their waiting time by $105$ units of time.
+Considering that each process in $Q_{1}$ is assigned a quantum value of $50$, as we reach the last process in $Q_{1}$, the total time elapsed equals $105$, which happens to be the time that all the other processes in the subsequent queues had to wait for, hence the addition of their waiting time by a value of $105$ units of time.
 
@@
 
-Even though $P_{5}$ is assigned to $Q_{3}$ as in Table \ref{table1}, it was promoted to $Q_{2}$ due to satisfying (\ref{eq1}).
+Even though $P_{5}$ is initially assigned to $Q_{3}$ as in Table \ref{table1}, it was promoted to $Q_{2}$ due to satisfying inequality (\ref{eq1}).
 
@@
 
-Whenever processes reach the lowest queue precompletion, they are scheduled using the RR scheduling algorithm with a relatively large quantum time value which is in most cases similar to using the FCFS algorithm because, as the time quantum value of the RR algorithm tends to infinity which could practically be a very large number relative to the available processes remaining time, the algorithm tends to morph into the FCFS algorithm.
-This procedure is repeated until all the processes are finished.
+Whenever processes reach the lowest queue precompletion, they are scheduled using the RR scheduling algorithm with a relatively large quantum time value which is in most cases similar to using the FCFS algorithm because, as the time quantum value of an RR algorithm tends to infinity which could practically be a very large number relative to the available processes remaining time values, the algorithm tends to morph into the FCFS algorithm.
+This procedure is iterated until all the processes are finished.
 Simulation results are shown in the table below:
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COMPARISONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Performance Comparisons}
 
-To assess the performance of the proposed algorithm implementation, a varying number of processes is taken in six different experiments as input to the Python simulation script.
-In each experiment, the output of the proposed algorithm implementation is compared to the output of another scheduling algorithm implementation such as standard MLFQ with static quantum RR and other variants of MLFQ and RR addressed in different papers.
+To assess the performance of the proposed algorithm implementation, multiple test cases are addressed and analyzed in seven different experiments.
+In each experiment, the output of the proposed algorithm implementation is compared to the output of another scheduling algorithm implementation addressed in a different paper, such as standard MLFQ algorithm with static quantum RR and other variants of MLFQ algorithms and RR algorithms.
 
@@
 
-In this experiment, the proposed algorithm is compared against an MLFQ algorithm stated in \cite{b4} that uses a static version of the RR algorithm for scheduling each queue and another variant that uses a dynamic version of the RR algorithm for doing so.
+In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b4}.
+The first uses a static version of the RR algorithm for scheduling each queue, while the second variant uses a dynamic version of the RR algorithm for doing so.
 
@@
      \end{tabular}
-     \label{table1}
 \end{table}
@@
 
-In this experiment, the proposed algorithm is compared against an MLFQ algorithm stated in \cite{b4} that uses a static version of the SJFRR algorithm for scheduling each queue and another variant that uses a dynamic version of the SJFRR algorithm for doing so.
+In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b4}.
+The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.
 
@@
 
-In this experiment, the proposed algorithm is compared against an MLFQ algorithm stated in \cite{b5} that uses a static version of the SJFRR algorithm for scheduling each queue and another variant that uses a dynamic version of the SJFRR algorithm for doing so.
+In this experiment, the proposed algorithm is compared against two MLFQ algorithm variants stated in \cite{b5}.
+The first uses a static version of the SJFRR algorithm for scheduling each queue, while the second variant uses a dynamic version of the SJFRR algorithm for doing so.
 
@@
 
-In this experiment, the proposed algorithm is compared against different variants of the MLFQ algorithm that are stated in \cite{b6}: standard MLFQ, a priority-based MLFQ and a vague logic-based MLFQ algorithm.
+In this experiment, the proposed algorithm is compared against multiple variants of the MLFQ algorithm that are stated in \cite{b6}: standard MLFQ algorithm, a priority-based MLFQ algorithm and a vague logic-based MLFQ algorithm.
 
@@
 
-This experiment is the same as the previous one but with a different input test case.
+This experiment is the same as the previous one, but with a different input test case.
 
@@
 
-This experiment is the same as the previous one but with a different input test case.
-Note that for this test case, a process queue number is irrelevant to both RR algorithm and SRBRR algorithm mentioned in \cite{b3}.
+This experiment is the same as the previous one, but with a different input test case.
+Note that for this test case, a process queue number is irrelevant to both the RR algorithm and the SRBRR algorithm mentioned in \cite{b3}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% OBSERVATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Observation}
+
 From the above simulations of different test cases and multiple performance comparisons that involved as many as 11 different scheduling algorithms not including this paper algorithm, it is clear that the average turnaround time and the average waiting time of the proposed algorithm is less than or – in few occasions  – nearly equal to those of the stated algorithms.
-With that said, the proposed algorithm is arguably advantageous over those algorithms, considering even the case in which it underperformed compared to the SRBRR algorithm, it is still favourable due to the capability to separate processes into categories based on their need for the processor and other advantages of the MLFQ algorithm.The performance of the proposed algorithm compared to other algorithms is further illustrated in the graphs below:
+With that said, the proposed algorithm is arguably advantageous over those algorithms, considering even the case in which it underperformed compared to the SRBRR algorithm, it is still favourable due to the capability to separate processes into categories based on their need for the processor and other advantages of the MLFQ algorithm.
+The performance of the proposed algorithm compared to other algorithms is further illustrated in the following graphs:
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion and Future Work}
@@
 The goal of this paper is to tackle different shortcomings associated with the standard MLFQ scheduling algorithm as well as its variants discussed in several papers.
-To resolve those deficiencies, we introduced different adjustable policies and techniques and it is evidently clear that those methods yield better CPU performance and optimize utilization by reducing the average waiting time as well as the average turnaround time.
-Despite experimenting numerous combinations of the parameters and scheduling policies by which an MLFQ algorithm operates, we can say that there is yet a large room for experiment and improvement through finding better methods and policies to make the algorithm more adaptable to the nature of the submitted processes and overall more enhanced.
+To resolve these deficiencies, we introduced different adjustable policies and techniques.
+It is evidently clear that those methods yield better CPU performance and optimize utilization by reducing the average waiting time as well as the average turnaround time.
+Despite experimenting numerous combinations of the parameters and scheduling policies by which the proposed MLFQ algorithm operates, we can say that there is yet a large room for experiment and improvement through finding better methods and policies which would make the algorithm more adaptable to the nature of the submitted processes and overall more enhanced.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-04-20 paper.tex
Paper is Now Publishable

@@
 \subsection{Pseudocode Flowchart of the Proposed Approach}
-\vspace{5mm}
-\begin{tikzpicture}[node distance=2cm]
+\begin{tikzpicture}[node distance=2.2cm]
 
@@
     \node (in1) [io, below of=start, text width = 2cm] {Read Processes Data};
-    \node (pro1) [process, below of=in1, text width = 3cm] {Assign processes to their respective queue};
-    \node (dec1) [decision, below of=pro1, text width = 2cm, yshift=-1cm] {All queues are empty};
-    \node (end) [startstop, left of=dec1, xshift=-2cm] {End};
-    \node (pro2) [process, below of=dec1, text width= 3cm, yshift = -1cm] {Iterate on non-empty queues $Q$};
-    \node (dec2) [decision, below of=pro2, text width = 2cm, yshift=-1cm] {A process $P_{j}$ in $Q_{i+1}$ is boostable};
-    \node (pro3) [process, left of=dec2, text width= 3cm, xshift= -2.2cm] {Promote $P_{j}$ to $Q_{i}$};
-    \node (pro4) [process, below of=dec2, text width= 3cm, yshift=-1.2cm] {Calculate the quantum time value $\Gamma$ of $Q_{i}$};
-    \node (pro5) [process, below of=pro4, text width= 3cm] {Assign $\Gamma$ to $Q_{i}$ processes};
-    \node (pro6) [process, below of=pro5, text width= 3cm] {Downgrade incomplete processes to $Q_{i+1}\,:\,i+1 < 5$};
-    \node (pro7) [process, below of=pro6, text width= 3cm] {Increment waiting time of $P_{j} \notin Q_{i}$};
+    \node (dec1) [decision, below of=in1, text width = 2cm, yshift=-1cm] {All processes are finished};
+    \node (pro1) [process, below of=dec1, text width= 3cm, yshift = -1cm] {Iterate on queues $Q$};
+    \node (pro2) [process, below of=pro1, text width = 3cm] {Assign eligable processes to the current queue};
+    \node (out1) [io, left of=dec1, text width = 2cm, xshift= -2cm] {Print avg. waiting time, avg. turnaround time, throughput};
+    \node (end) [startstop, below of=out1, yshift=-1cm] {End};
+    \node (dec2) [decision, below of=pro2, text width = 2cm, yshift=-2cm] {A process $P$ in the subsequent queue is boostable};
+
+    \node (pro3) [process, left of=dec2, text width= 3cm, xshift= -2.5cm] {Promote $P$ to current queue};
+    \node (pro4) [process, below of=dec2, text width= 3cm, yshift=-2.2cm] {Calculate the quantum time value $\phi$};
+    \node (pro5) [process, below of=pro4, text width= 3cm] {Schedule processes in current queue};
 
     \draw [arrow] (start) -- (in1);
-    \draw [arrow] (in1) -- (pro1);
-    \draw [arrow] (pro1) -- (dec1);
-    \draw [arrow] (dec1) -- node[anchor=west, above] {Yes} (end);
-    \draw [arrow] (dec1) -- node[anchor=south, left] {No} (pro2);
+    \draw [arrow] (in1) -- (dec1);
+    % \draw [arrow] (pro1) -- (dec1);
+    \draw [arrow] (dec1) -- node[anchor=west, above] {Yes} (out1);
+    \draw [arrow] (out1) -- (end);
+    \draw [arrow] (dec1) -- node[anchor=south, left] {No} (pro1);
+    \draw [arrow] (pro1) -- (pro2);
     \draw [arrow] (pro2) -- (dec2);
     \draw [arrow] (dec2) -- node[anchor=west,above] {Yes} (pro3);
-    \draw [arrow] (pro3.north) -- ++ (0,1.3) -- ++ (4.2,0);
+    \draw [arrow] (pro3.north) -- ++ (0,3.7) -- ++ (3.1,0);
     \draw [arrow] (dec2) -- node[anchor=south, left] {No} (pro4);
     \draw [arrow] (pro4) -- (pro5);
-    \draw [arrow] (pro5) -- (pro6);
-    \draw [arrow] (pro6) -- (pro7);
-    \draw [arrow] (pro7.west) -- ++ (-4.5,0) -- ++(0,16.8) -- ++(6.1,0);
-
+    \draw [arrow] (pro5.east) -- ++ (1.2,0) -- ++(0,16.2) -- ++(-1.3,0);
     \end{tikzpicture}
@@
 \subsection{Proposed Algorithm}
-\floatstyle{norules}
+% \floatstyle{norules}
 \restylefloat{algorithm}
 \begin{algorithm}[H]
-    \caption{Enhanced Multilevel FeedBack Queue Scheduling Algorithm}
+    \caption{Developed Multilevel Feedback Queue Scheduling Algorithm}
+    \hspace*{\algorithmicindent} \textbf{Input:} Number of processes $n$, processes priority $\alpha$\\
+    \hspace*{\algorithmicindent} burst time values $\beta$, arrival time values $\sigma$, \\
+    \hspace*{\algorithmicindent} context switching cost $\epsilon$\\
+    \hspace*{\algorithmicindent} \textbf{Output:} Average turnaround time, average waiting time,\\
+    \hspace*{\algorithmicindent} throughput
     \begin{algorithmic}[1]
-    \Procedure {EMLFQ}{Number of processes $n$, priority of each process $\alpha_{i}$, burst time of each process $\beta_{i}$}
+    \Procedure {DMLFQ}{}
     % Return  Average waiting time, throughput
     \Statex Declaration and Initialisation:
-    \State Queue $Q_{i}$ where $i \in \{0, 1, 2, 3, 4\}$, waiting time $\omega_{i} = 0$ of $P_{i}$, quantum time $\Gamma$, quantum time index $\gamma$
-        \For {$i = 0$ to $n$}
-            \State \textbf{Assign} $P_{i}$ to $Q_{\alpha_{i}}$
-        \EndFor
-    \Statex Loop Process:
-        \State $i = 0$
-        \While {$Q_{i}$ is NOT empty}
-            % Aging Processes
-            \For{$j = i + 1$ to $5$}
-                \If{$1-\omega_{\theta}/\beta_{\theta} < 0.95$ for $\theta \in Q_{j}$}
-                    \State \textbf{Promote} $P_{\theta}$ to the current queue $Q_{i}$
+    \State Queue $Q_{i}$ where $i \in \{1, 2, 3, 4, 5\}$
+    \State Turnaround time values $\tau$
+    \State Finish time values $\lambda$
+    \State Waiting time values $\theta$
+    \State Remaining time values $\mu = \beta$
+    \State Quantum time value $\phi$
+    \State Number of context switches $\delta$
+        \State$time = 0$
+        \While{$\exists P \in Q$}
+            \For{$i = 1$ to $5$}
+                \For{$j = 1$ to $n$}
+                    \If{$\sigma_{j} <= time$ and $\alpha_{j}$ equals $i$}
+                        \State \textit{\textbf{Assign}} $P_{j}$ to $Q_{i}$
+                    \EndIf
+                    \State $waitingTime = time - \sigma_{j}$
+                    \If{$i < 5$ and $waitingTime/\mu_{j} >= 1$ and $\alpha_{j}$ equals $i + 1$ and  $\sigma_{j} <= time$}
+                        \State \textit{\textbf{Assign}} $P_{j}$ to $Q_{i}$
                     \EndIf
                 \EndFor
-
-            % Calculating the quantum time value
-            \Statex Calculating the quantum time value:
-            \State $ascending\_sort(\beta_{Q_{i}})$
-            \State $\gamma = Q_{i}.size()/2 + i$
-            \State $\Gamma = \beta_{\gamma}$ where $\beta_{\gamma} \in Q_{i}$
-            % Assigning the quantum value to each process in the queue
-            \Statex Assigning the Quantum Value to each Process:
-            \For{$P_{j}$ in $Q_{i}$}
-                \State $\beta_{j} = \beta_{j} - \Gamma$
-                \If{$\beta_{j} <= 0$}
-                    \State \textbf{Remove} $P_{j}$ from $Q_{i}$
-                \ElsIf {$i < 4$}
-                    \State \textbf{Downgrade} $P_{j}$ to $Q_{i+1}$
+                \State Sort $Q_{i}$ in ascending order according to remaining time values
+                \State $\phi = median\; value\; of\; Q_{i} * i$
+                \algrenewcommand\algorithmicfor{\textbf{foreach}}
+                \For{$P_{j} \in Q_{i}$}
+                    \If{$\mu_{j} <= \phi$}
+                        \State $time = time + \mu_{j}$
+                        \State $\lambda_{j} = time$
+                        \State \textit{\textbf{Remove}} $P_{j}$ from $Q_{i}$
+                    \Else
+                        \State $time = time + \phi$
+                        \State $\mu_{j} = \mu_{j} - \phi$
+                        \If{$i < 5$}
+                            \State $\alpha_{j} = \alpha_{j} + 1$
+                        \EndIf
+                    \EndIf
+                    \If{Previous process $\neq P_{j}$}
+                        \State $time = time + \epsilon$
+                        \State $\delta = \delta + 1$
                     \EndIf
                 \EndFor
-            % Increment waiting time
-            \Statex Increment Waiting Time:
-            \For{$j = 0$ to $n$ \textbf{and} $P_{j} \notin Q_{i}$}
-                \State $\omega_{j} = \omega_{j} + 1$
+                \algrenewcommand\algorithmicfor{\textbf{for}}
             \EndFor
-            \Statex Increment Queue Index
-            \If{$i < 4$}
-                \State $i = i + 1$
-            \EndIf
         \EndWhile
+        \For{$i = 1$ to $n$}
+            $\tau_{j} = \lambda_{j} - \sigma_{j}$, $\theta_{j} = \tau_{j} - \beta_{j}$
+        \EndFor
+        \State \textbf{return} average of $\theta$, average of $\tau$, $n/time$
         \EndProcedure
@@
 Each process is assumed to have its own predetermined burst time, arrival time and the queue to which each one belongs.
+The proposed approach is non-preemptive.
+For the sake of giving an example, if a process was lately introduced to a queue denoted by $Q_{i}$ prior to the current queue getting scheduled, it won't get scheduled until the current queue, its subsequent queues and the queues prior to $Q_{i}$ get scheduled.
 
@@
 
-\vspace{4mm}
+% \vspace{4mm}
 
@@
 
+    \legend{Proposed Algorithm,Dynamic RR MLFQ, Static RR MLFQ, Dyn.
+SJFRR MLFQ of \cite{b4},  Stat.
+SJFRR MLFQ of \cite{b4}, Dyn.
+SJFRR MLFQ of \cite{b5}, Stat.
+SJFRR MLFQ of \cite{b5}, VMLFQ, MLFQ, PMLFQ, Dynamic SRBRR, Static RR}
     \end{axis}
@@
 \caption{Comparison graph for average turnaround time}
+\vspace{45mm}
 \end{figure}
@@
 Despite experimenting numerous combinations of the parameters and scheduling policies by which the proposed MLFQ algorithm operates, we can say that there is yet a large room for experiment and improvement through finding better methods and policies which would make the algorithm more adaptable to the nature of the submitted processes and overall more enhanced.
+For instance, adjusting the criteria by which the schedular decides whether to promote a process might further lessen starvation.
+Making the proposed algorithm preemptive might also aid mitigating starvation and render overall better performance.
+The possibilities are limitless.
 

### 2020-04-21 paper.tex
Add Missing Comma

@@
 
-\author{\IEEEauthorblockN{Nader AbdAlGhani\IEEEauthorrefmark{1}
-Mahmoud Mohamad\IEEEauthorrefmark{2}, Muhanad Atef\IEEEauthorrefmark{3} and Khaled Amgad\IEEEauthorrefmark{4}}
+\author{\IEEEauthorblockN{Nader AbdAlGhani\IEEEauthorrefmark{1}, Mahmoud Mohamad\IEEEauthorrefmark{2}, Muhanad Atef\IEEEauthorrefmark{3} and Khaled Amgad\IEEEauthorrefmark{4}}
 \IEEEauthorblockA{Computer Engineering Dept.,
